### 2025-02-26 paper/sections/ExperimentalSetup.tex
solved supervisor comments

Preprocessing of the dataset was performed using the \texttt{clean-text} library. The preprocessing pipeline involved multiple steps to clean and standardize the text data. Initially, all text was converted to lowercase, and unnecessary whitespace was removed to eliminate redundancy. Special characters, URLs, and emojis were filtered out using regular expressions, with emojis being replaced by their corresponding textual descriptions (e.g., \smiley $\rightarrow$ ``smiling face''). Punctuation was also removed, and  tokenization was performed using language-specific tokenizers to ensure optimal segmentation, and stopwords were removed to further reduce noise. These steps ensured the data was clean and consistent across all subsets. Preprocessing was applied consistently to the training, validation, and test datasets to avoid introducing biases or inconsistencies. Such preprocessing steps have been shown to improve the performance of NLP models by reducing noise and simplifying the input representations \citep{Zhang2020DataPrep}.

@@

The model training process relied on Binary Cross-Entropy (BCE) as the loss function for Track A and C, and Cross-Entropy for Track B due to its suitability for classification tasks. Given the unbalanced dataset, a weighted loss approach was employed to ensure that the model adequately learned from all classes. Optimization for fine-tuning deep learning models was performed using the \texttt{AdamW} optimizer, which improves upon the standard Adam optimizer by decoupling weight decay and learning rate updates \citep{Loshchilov2019AdamW}. To further enhance training stability and convergence, a cosine annealing learning rate scheduler with restarts\cite{loshchilov2017sgdrstochasticgradientdescent} was employed. This scheduling approach helped adaptively reduce the learning rate over time, facilitating better exploration of the loss landscape and improving generalization. The model was trained for a fixed number of epochs, and early stopping was used to terminate training if the validation performance plateaued, thus avoiding overfitting.

>>>>

Preprocessing of the dataset was performed using the \texttt{clean-text} library. The preprocessing pipeline involved multiple steps to clean and standardize the text data. Initially, all text was converted to lowercase, and unnecessary whitespace was removed to eliminate redundancy. Special characters, URLs, and emojis were filtered out using regular expressions. Emojis were replaced by their corresponding textual descriptions (e.g., \smiley $\rightarrow$ ``smiling face''). Punctuation was also removed, and  tokenization was performed using language-specific tokenizers to ensure optimal segmentation, and stopwords were removed to further reduce noise. These steps ensured the data was clean and consistent across all subsets. Preprocessing was applied consistently to the training, validation, and test datasets to avoid introducing biases or inconsistencies. Such preprocessing steps have been shown to improve the performance of NLP models by reducing noise and simplifying the input representations \citep{Zhang2020DataPrep}.

@@

The model fine-tuning with LoRA, and the training of the MLP and XGBoost models, utilized Binary Cross-Entropy (BCE) as the loss function for Tracks A and C, and Cross-Entropy for Track B, owing to its appropriateness for classification tasks. Meanwhile, the training of the SVM model employed hinge loss.Using LoRA, we fine-tuned the Q, K, and V matrices for feature extractor transformer models, as shown in Table \ref{tab:model_selection}. Given the unbalanced dataset, a weighted loss approach was employed to ensure that the model adequately learned from all classes. Optimization for fine-tuning deep learning models was performed using the \texttt{AdamW} optimizer, which improves upon the standard Adam optimizer by decoupling weight decay and learning rate updates \citep{Loshchilov2019AdamW}. To further enhance training stability and convergence, a cosine annealing learning rate scheduler with restarts\cite{loshchilov2017sgdrstochasticgradientdescent} was employed. This scheduling approach helped adaptively reduce the learning rate over time, facilitating better exploration of the loss landscape and improving generalization. The model was trained for a fixed number of epochs, and early stopping was used to terminate training if the validation performance plateaued, thus avoiding overfitting.

### 2025-02-26 paper/sections/RelatedWork.tex
solved supervisor comments

\section{Related Work}
Multi-label emotion detection has emerged as a significant task in natural language processing (NLP), particularly for low-resource languages. The task is structured in two main output formats: (1) a binary format, which indicates whether an emotion is present in the text, and (2) an intensity scale ranging from 0 to 3, which represents the strength of the emotion in the text.

Given that this task follows a text classification paradigm, various models have been explored to identify the most effective architectures. A considerable amount of research has focused on evaluating different structures to determine the optimal approach. In \cite{wang2016dimensional}, a combination of Long Short-Term Memory (LSTM) networks and Convolutional Neural Networks (CNNs) was explored, where various model configurations were compared based on their F1-score performances. These insights were leveraged to identify suitable model structures for developing a custom model tailored to the specific requirements of this task.

>>>>

\section{Related Work}
Multi-label emotion detection has emerged as a significant task in NLP\footnote{natural language processing}, particularly for low-resource languages. The task is structured in two main output formats: (1) a binary format, which indicates whether an emotion is present in the text, and (2) an intensity scale ranging from 0 to 3, which represents the strength of the emotion in the text.

Given that this task follows a text classification paradigm, various models have been explored to identify the most effective architectures. A considerable amount of research has focused on evaluating different structures to determine the optimal approach. In \cite{wang2016dimensional}, a combination of LSTM\footnote{Long Short-Term Memory} networks and CNNs\footnote{Convolutional Neural Networks} was explored, where various model configurations were compared based on their F1-score performances. These insights were leveraged to identify suitable model structures for developing a custom model tailored to the specific requirements of this task.

### 2025-02-26 paper/sections/SystemOverview.tex
solved supervisor comments

The preprocessing pipeline involves several steps to clean and standardize the text data. These include converting text to lowercase, removing unnecessary whitespace, filtering out special characters, URLs, and emojis by replacing with their textual description, normalizing tokens, performing language-specific tokenization, and removing stopwords. These steps ensure the data is consistent and suitable for NLP\footnote{natural language processing} tasks.

@@

To extract features, we employed a diverse range of models, including LSTM\footnote{Long Short-Term Memory} networks, MLMs\footnote{Multilingual Language Models}, and LLMs\footnote{Large Language Models}. The LLMs were fine-tuned using LoRA\footnote{Low-Rank Adaptation} \citep{hu2021lora}, a parameter-efficient tuning method that facilitates task-specific adaptation while maintaining computational efficiency.

@@

\subsection{Summary of Model Variants}

By combining these techniques, the proposed system captures rich linguistic representations of the input text and achieves accurate multi-label classification. The experimental setup and evaluation metrics used to validate the effectiveness of this approach are discussed in subsequent sections.

>>>>

The preprocessing pipeline involves several steps to clean and standardize the text data. These include converting text to lowercase, removing unnecessary whitespace, filtering out special characters, URLs, and emojis by replacing with their textual description, normalizing tokens, performing language-specific tokenization, and removing stopwords. These steps ensure the data is consistent and suitable for NLP tasks.

@@

To extract features, we employed a diverse range of models, including LSTM networks, MLMs\footnote{Multilingual Language Models}, and LLMs\footnote{Large Language Models}. The LLMs were fine-tuned using LoRA\footnote{Low-Rank Adaptation} \citep{hu2021lora}, a parameter-efficient tuning method that facilitates task-specific adaptation while maintaining computational efficiency.

@@

% \subsection{Summary of Model Variants}

% By combining these techniques, the proposed system captures rich linguistic representations of the input text and achieves accurate multi-label classification. The experimental setup and evaluation metrics used to validate the effectiveness of this approach are discussed in subsequent sections.
